Titulo

### 2015-02-25 RotacionOutFlows/Paper/ms.tex
Max cite and reordering paragraphs

To fully understand the observed spectra of the LAEs this galaxies must be
modeled. However the resonant nature of the lines makes this a challenging
task. Analytical solutions for the outcoming spectra in simple ISM static
geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
  Dijkstra06}. Recent hydrodynamical simulations have studied the
outcomming spectra of LAEs in large scale simulations, while some
others have studied detailed galaxies \citep{Verhamme12}.  
Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been
used in order to understand the effect of the  gas kinematics in the
Line, special attention have been devoted to model the presence   of
outflows in the galaxy. Here different models have attempt to 
simulate more realistic situations involving shlle models, cavities and-- 
\citep{Behrens2014}. Most recently \cite{Garavito14} have studied in 
detail the effect of rotation on the lyman alpha line.

As many previous studies have shown outflows are present in LAEs
(\textbf{References}), the outflows are mainly a consecuence of the
intergalactic medium (IGM) being ejected  from the galaxy due to
supernova explotions. 
However rotation should also be present in this galaxies. The joint
effect of the two above properties should have a direct effect on the
morphology of the \lya line.

This effect is the motivation of this paper in which we combine the
effect of rotation  follow by an outflow. We proposed a simplyfied
model in which the galaxy is modeled as an sphere, with an homogeneous
mixture of dust and hydrogen at a constant temperature and undergoing
solid-body rotation.

>>>>

To fully understand the observed spectra of the LAEs this galaxies must be
modeled. However the resonant nature of the lines makes this a challenging
task. Analytical solutions for the outcoming spectra in simple ISM static
geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
  Dijkstra06}.Most recently \cite{Garavito14} have studied in
detail the effect of rotation on the lyman alpha line.
Hydrodynamical simulations have studied the
outcomming spectra of LAEs in large scale simulations, while some
others have studied detailed galaxies \citep{Verhamme12}.  
Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been
used in order to understand the effect of the gas kinematics in the
\lya line.

Especial attention have been devoted to model the presence of
outflows in the galaxy, motivates by previous observational 
studies . Outflows are a consecuence of the
intergalactic medium (IGM) being ejected from the galaxy due to
supernova explotions. Here different models have attempt to 
simulate more realistic situations involving shell models and cavities. 
\citep{Behrens2014}.

Despite the fact that outflows have been broadly studied 
rotation should also be present in this galaxies. T
he joint effect of the two above properties should have 
a direct effect on the morphology of the \lya line.

Study this effect is the main motivation of this paper in which we combine the
effect of rotation followed by an outflow. We proposed a simplyfied
model in which the galaxy is modeled as an sphere undergoing
solid-body rotation, with an homogeneous mixture of dust and 
hydrogen at a constant temperature.
